### 2019-11-13 paper/paper.tex
Add optimizer to arguments

\begin{algorithm}[!htb]
\DontPrintSemicolon
\SetAlgoLined
\KwIn{Initial Guess of the Scene Parameters, Maximum Number of Iterations, Tolerance in Loss}
\KwOut{Optimized set of Scene Parameters}
params $\gets$ Initial Guess of Scene Parameters\;
tolerance $\gets$ Tolerance in Loss\;
max\_iter $\gets$ Maximum Number of Iterations\;
converged $\gets$ false\;
iter $\gets$ 0\;
\While{not \textbf{converged} or iter < max\_iter}{
    loss $\gets$ mean\_squared\_loss (render\_image (params), target\_img)\;
    gs $\gets$ gradient(loss)\;
    \For{param in params}{
        update! (optimizer, param, gs[param])\;
    }
    \If{loss < tolerance}{
        converged $\gets$ true\;
    }
    iter $\gets$ iter + 1\;
}
\Return{params}\;
\caption{Gradient Based Optimization of Scene Parameters}
\label{alg:inv_render}
\end{algorithm}

>>>>

\begin{algorithm}[!htb]
\DontPrintSemicolon
\SetAlgoLined
\KwIn{Initial Guess of the Scene Parameters, Maximum Number of Iterations, Tolerance in Loss, First-Order Optimization Algorithm}
\KwOut{Optimized set of Scene Parameters}
params $\gets$ Initial Guess of Scene Parameters\;
tolerance $\gets$ Tolerance in Loss\;
max\_iter $\gets$ Maximum Number of Iterations\;
optimizer $\gets$ First-Order Optimization Algorithm\;
converged $\gets$ false\;
iter $\gets$ 0\;
\While{not \textbf{converged} or iter < max\_iter}{
    loss $\gets$ mean\_squared\_loss (render\_image (params), target\_img)\;
    gs $\gets$ gradient(loss)\;
    \For{param in params}{
        update! (optimizer, param, gs[param])\;
    }
    \If{loss < tolerance}{
        converged $\gets$ true\;
    }
    iter $\gets$ iter + 1\;
}
\Return{params}\;
\caption{Gradient Based Optimization of Scene Parameters}
\label{alg:inv_render}
\end{algorithm}
